%                                                                 aa.dem
% AA vers. 8.2, LaTeX class for Astronomy & Astrophysics
% demonstration file
%                                                       (c) EDP Sciences
%-----------------------------------------------------------------------
%
%\documentclass[referee]{aa} % for a referee version
%\documentclass[onecolumn]{aa} % for a paper on 1 column  
%\documentclass[longauth]{aa} % for the long lists of affiliations 
%\documentclass[rnote]{aa} % for the research notes
%\documentclass[letter]{aa} % for the letters 
%\documentclass[bibyear]{aa} % if the references are not structured 
% according to the author-year natbib style

%
\documentclass{aa}  

%
\usepackage{graphicx}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{txfonts}
\input{macros}		% file containing author's macro definitions
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\usepackage[options]{hyperref}
% To add links in your PDF file, use the package "hyperref"
% with options according to your LaTeX or PDFLaTeX drivers.
%
\begin{document} 


   \title{New \formaldehyde Maser in G0.38+0.04}

   \subtitle{}

   \author{Getal}

   \institute{institoot}

   \date{whatdate}

% \abstract{}{}{}{}{} 
% 5 {} token are mandatory
 
  \abstract
   {We have found a new \formaldehyde \oneone (formaldehyde) maser in the Galactic
Center Cloud C, G0.38+0.04.  At the time of publication, this is the eighth
region containing a \formaldehyde detected in the galaxy.  Cloud C is the only
region of confirmed high-mass star formation along the Galactic Center Ridge,
further confirming that \formaldehyde masers are exclusively associated with high-mass
star formation.
}

   \keywords{  }

   \maketitle

%Extragalactic masers:
%Arp 220 Baan1986a
%NGC 6240 Wang2013a 2013RAA....13..270W



\section{Introduction}
Masers are important tracers of star formation, shocked gas, evolved stars, and
in other galaxies, circumnuclear disks.  While many masers are very common in
the Galaxy and readily detected in other galaxies (e.g., OH, \methanol,
\water), \formaldehyde has only been detected in emission in 7 locations within
our galaxy, and so far none in other galaxies \citep{Araya2007c,Mangum2008a}.

Most of the \formaldehyde masers so far detected have been observed as part of
dedicated surveys targeting high-mass young stellar objects
\citep{Araya2004a,Araya2007b,Araya2008a}.  Despite concerted effort, very few
new masers have been discovered since their initial discovery in
\citet{Forster1980a}, including many in Sgr B2
\citep{Whiteoak1983a,Mehringer1994b}.  All of the known \formaldehyde masers
are associated with regions of high-mass star formation
\citep{Pratap1994a,Araya2004a,Araya2007b,Araya2008a}.
% Forster et al. 1980, Whiteoak & Gardner 1983, Pratap et al. 1994,


\section{Observations}
ATCA observations were performed in 2015 as part of a larger survey.

\section{Analysis}
We detect one narrow line ($\sigma<1.3$ \kms, below the instrument resolution)
at $v=36.7$ \kms with an amplitude of 235 mJy/beam, where the restoring beam is
$4.84\arcsec\times1.49\arcsec$.  This translates to a brightness temperature of
1700 K, which is far brighter than thermal \formaldehyde emission should ever
reach.  It is also unresolved, so this brightness temperature is a lower limit.

The maser line is probably not detectable by single-dish observations.  Cloud C
is part of a dense and extended cloud that is strongly detected in absorption,
either against the CMB or the local background continuum.  This absorption has
a comparable flux density to the emission at the best available single-dish resolution
for CMZ sources ($\sim3\arcmin$).  However, with $\sim1\arcmin$ resolution, the 
emission would still be detectable, so larger dishes, e.g. Arecibo and FAST,
could detect similar sources.  However, extragalactic detections of such weak
masers is extremely unlikely.

\section{Discussion}
Out of the 8 known maser-containing regions in the Galaxy, there are now two in
the Central Molecular Zone.  These two regions, Cloud C and Sgr B2, are the only
dense clouds in the CMZ with known high-mass star formation.  Sgr C also shows
some hints of high-mass star formation \citep{Kendrew2013a}, but it has not yet
been searched for \formaldehyde masers.

This high detection rate within the CMZ, despite limited statistical
information, is suggestive that \formaldehyde masers may be an efficient tracer
of high-mass star formation in extreme environments.
It also raises questions: What is different about CMZ high-mass star formation and
similar star formation in other parts of the galaxy?  Extensive surveys have shown
that the occurrence of \formaldehyde masers in ``normal'' high-mass star
forming regions in the Galaxy is very low, $<2\%$, or 1 of 58 sources in a
large survey \citep{Araya2004a,Araya2007b,Araya2008a}\footnote{In a large unpublished survey
of 400 sources with the GBT, there are no new maser detections}.  

Other masers have been detected in Cloud C.  \methanol, \water, and OH have all
been observed with ATCA, and they coincide to within the absolute positional
accuracy of ATCA of 0.5\arcsec
\citep[][respectively]{Caswell2010a,Walsh2014a,Argon2000a}.  Clearly, this is
an amasering region.  Maybe we should look for SiO and \ammonia masers next.

%TODO
%-Other masers in Cloud C?
%  YES: methanol (our data, Caswell 1996)
%  YES: water (Walsh 2011, 2014)
%  YES: OH (Argon2000a)
  
\end{document}



